Medical Concept Extraction

### 2012-12-17 paper/paper.tex
Final pass complete.

\item {\tt models/<model-name>/test_predictions/} - Contains output files with the predicted label for each word in the input file.

@@

As priorly mentioned, we tested our feature set using three classifiers in search of the best concept extraction system (general SVM, linear SVM, and CRF), all of which yielded comparable results in terms of their average F1 scores, but showed significant difference in terms of efficiency. Our less efficient classifier was eventually eliminated from our system, as discussed in the subsequent section.

@@

Our more extensive tests also revealed that our baseline F1 score is primarily a reflection of the inclusion of a single feature: the word itself.  In that sense, much of our performance can be credited purely to machine learning with one particularly strong feature. However, our additional improvements on this score required more in-depth linguistic analysis of our training data. Moreover, all of our machine learning algorithms showed comparable improvements with more language-driven features--these features show a measure of success that is independent from the chosen canned classifier. Nevertheless, we can always argue for a more eloquent implementation of our system in spite of our successful results.

@@

\begin{itemize}
\item First, we used stemming to add additional features to each word much in the same way that the word feature was created. However, after performing more complete feature selection we would have liked to select the best suited stemmer and used that in place of the word feature.

@@

While the second approach exhibits only a modest reduction (and may be taken care of automatically by some stemmers), the first and third approaches may allow us to dramatically reduce the dimension of the problem. Our hypothesis is that this will certainly improve the runtime performance, and perhaps the classification performance as well.

>>>>

\item {\tt models/<model-name>/test\_predictions/} - Contains output files with the predicted label for each word in the input file.

@@

As priorly mentioned, we tested our feature set using three classifiers in search of the best concept extraction system (general SVM, linear SVM, and CRF), all of which yielded comparable results in terms of their average F1 scores, but showed significant difference in terms of efficiency. Our least time efficient classifier, SVM, was eventually eliminated from our system, as discussed in the subsequent section.

@@

Our more extensive tests also revealed that our baseline F1 score is primarily a reflection of the inclusion of a single feature: the word itself.  In that sense, much of our performance can be credited purely to machine learning with one particularly strong feature. However, our additional improvements on this score required more in-depth linguistic analysis of our training data. Moreover, all of our machine learning algorithms showed comparable improvements with more language-driven features. Therefore, these features indicate a measure of success that is independent from the chosen canned classifier. Nevertheless, we can always argue for a more eloquent implementation of our system in spite of our successful results.

@@

\begin{itemize}
\item First, we used stemming to add additional features to each word much in the same way that the word feature was created. However, after performing more complete feature selection we would have liked to select the best suited stemmer and use that in place of the word feature.

@@

While the second approach exhibits only a modest reduction (and may be taken care of automatically by some stemmers), the first and third approaches may allow us to dramatically reduce the dimension of the problem. Our hypothesis is that this will certainly improve the runtime performance, and perhaps the classification performance and model generalization as well.
